Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-03-29 manuscript/appC.tex
updates collated qbm 1-step oos

\author{}
\date{}
\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\doublespacing

@@

\section{Supplementary Information: Do we need detailed demographic data
to forecast population responses to climate
change?}\label{supplementary-information-do-we-need-detailed-demographic-data-to-forecast-population-responses-to-climate-change}

\subsubsection{Andrew T. Tredennick and Peter B.
Adler}\label{andrew-t.-tredennick-and-peter-b.-adler}

\emph{Andrew T. Tredennick
(\href{mailto:atredenn@gmail.com}{\href{mailto:atredenn@gmail.com}{atredenn@gmail.com}}),
Department of Wildland Resources and the Ecology Center, Utah State
University, Logan, UT}

\emph{Peter B. Adler, Department of Wildland Resources and the Ecology
Center, Utah State University, Logan, UT}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S1.pdf}
\caption{Posterior means (vertical ticks), 75\% credible intervals
(heavy lines), and 95\% credible intervals (light lines) of climate
effects on growth at both levels of inferences. The dashed vertical line
is at 0, indicating no effect.}
\end{figure}

>>>>

\author{}
\date{}
\usepackage{lineno}
\linenumbers
\usepackage{setspace}

@@

\renewcommand\thefigure{C\arabic{figure}}

\section{Appendix C: Effect of recruitment on IPM
uncertainty}\label{appendix-c-effect-of-recruitment-on-ipm-uncertainty}

In Fig. 4 of the main text where we show the uncertainty around our
models' forecasts to a 1\% change in climate covariates, the obvious
outlier is \emph{Pascopyrum smithii} (PASM). The uncertainty around PASM
forecasts from the integral projection model is orders of magnitude
larger than for any other species, and is even larger than the
uncertainty around the quad-based model forecasts. It turns out that the
estimated dispersion parameter for the negative binomial distribution is
much higher for PASM than for other species (Appendix B). This is
because PASM has higher recruitment rates than the other species and the
relationship between number of recruits and quadrat cover (see main
text) is weak. So, when we draw parameters from the MCMC chain for our
simulations, even larger values for the dispersion parameter are
possible. Thus, there can be very large ``boom'' years where recruitment
is high. When we allow all parameters to vary except those associated
with recruitment, uncertainty around PASM decreases to levels similar to
those associated with other species (Fig. C1).

\begin{figure}[htbp]
\centering
\includegraphics{appC/figure/appC-plot_it.pdf}
\caption{Mean (points) and 90\% quantiles (errorbars) for the
proportional difference between baseline simulations (using observed
climate) and the climate pertubation simulation on the x-axis. We
calculated proportional difference as log(perturbed climate cover) -
log(observed climate cover), where `perturbed' and `observed' refer to
the climate time series used to drive interannual variation in the
simulations. Model error and parameter uncertainty were propagated
through the simulation phase for all vital rates except recruitment.}
\end{figure}

### 2016-03-29 manuscript/appD.tex
updates collated qbm 1-step oos

\renewcommand\thefigure{C\arabic{figure}}

\section{Appendix C: Effect of recruitment on IPM
uncertainty}\label{appendix-c-effect-of-recruitment-on-ipm-uncertainty}

In Fig. 4 of the main text where we show the uncertainty around our
models' forecasts to a 1\% change in climate covariates, the obvious
outlier is \emph{Pascopyrum smithii} (PASM). The uncertainty around PASM
forecasts from the integral projection model is orders of magnitude
larger than for any other species, and is even larger than the
uncertainty around the quad-based model forecasts. It turns out that the
estimated dispersion parameter for the negative binomial distribution is
much higher for PASM than for other species (Appendix B). This is
because PASM has higher recruitment rates than the other species and the
relationship between number of recruits and quadrat cover (see main
text) is weak. So, when we draw parameters from the MCMC chain for our
simulations, even larger values for the dispersion parameter are
possible. Thus, there can be very large ``boom'' years where recruitment
is high. When we allow all parameters to vary except those associated
with recruitment, uncertainty around PASM decreases to levels similar to
those associated with other species (Fig. C1).

\begin{figure}[htbp]
\centering
\includegraphics{appC/figure/appC-plot_it.pdf}
\caption{Mean (points) and 90\% quantiles (errorbars) for the
proportional difference between baseline simulations (using observed
climate) and the climate pertubation simulation on the x-axis. We
calculated proportional difference as log(perturbed climate cover) -
log(observed climate cover), where `perturbed' and `observed' refer to
the climate time series used to drive interannual variation in the
simulations. Model error and parameter uncertainty were propagated
through the simulation phase for all vital rates except recruitment.}
\end{figure}

>>>>

\renewcommand\thefigure{D\arabic{figure}}

\section{Appendix D: Model forecasts without parameter
uncertainty}\label{appendix-d-model-forecasts-without-parameter-uncertainty}

In the main text we show results from model forecasts where we included
full model and parameter uncertainty (Fig. 6). However, the typical
approach in ecology is to use point estimates of model parameters and
only include model error. For example, to predict population size
\emph{N} at time \emph{t+1} one could do the following:

\begin{align}
\mu_{t+1} &= f(N_{t}) \\
N_{t+1} &\sim \text{Normal}(\mu_{t+1}, \sigma^2)
\end{align}

where $f(N_t)$ is some determinstic process (e.g., a linear regression
model) and $\sigma^2$ is the model error. Simulating populations in such
a way ignores variation in the parameters of $f(N_t)$. When we take this
approach to making forecasts of equilibrium cover under 1\% climate
perturbations the IPM and QBM make opposing predictions if we simply
look at the mean projection (Fig. D1). For both models, precision is
also artificially high (Fig. D2 and D3), since we know that parameter
uncertainty reduces forecast precision considerably (Fig. 6 in the main
text). All three presentations of model results (mean projection, mean
projection with model error, and forecasts with full uncertainty) can be
found in the literature, which is why we present them here as well.
However, as we state in the main text, true forecasts should only be
presented as we did in Fig. 6 of the main text.

\begin{figure}[htbp]
\centering
\includegraphics{appD/figure/appD-figure_d1.pdf}
\caption{Projected proportional changes in equilibrium cover caused by a
1\% increase in observed precipitation (+ppt), temperature (+temp), or
both (+ppt\&temp) as predicted by the individual-level IPM and the
population-level QBM using mean parameter values.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{appD/figure/appD-figure_d2.pdf}
\caption{Projected mean (points) proportional changes in equilibrium
cover and associated 90\% quantiles (errorbars) caused by a 1\% increase
in observed precipitation (+ppt), temperature (+temp), or both
(+ppt\&temp) as predicted by the individual-level IPM using mean
parameter values. Dashed line indicates proportional change of 0.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{appD/figure/appD-figure_d3.pdf}
\caption{Projected mean (points) proportional changes in equilibrium
cover and associated 90\% quantiles (errorbars) caused by a 1\% increase
in observed precipitation (+ppt), temperature (+temp), or both
(+ppt\&temp) as predicted by the population-level QBM using mean
parameter values. Dashed line indicates proportional change of 0.}
\end{figure}
